---
title: "Lab 3"
author: "Lucas Brack"
date: "January 29, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
```{r}
#install.packages("tidyverse")
library(tidyverse)
source("http://www.openintro.org/stat/data/cdc.R")
cdc <- as_tibble(cdc)
summary(cdc)

```


```{r}
ggplot(data = cdc, aes(x = smoke100, fill=as.factor(hlthplan)))+
  geom_bar(bins = 2)+
  labs(title ="Smokers Have Heath Coverage at a Lower Rate than Non-smokers", x = "Non-Smokers vs Smokers") +
   theme_minimal()  +
  scale_fill_discrete(name = "Health Coverage", labels = c("No", "Yes"))
```
This plot compares the health coverage of smokers against the coverage of non-smokers. I did this by creating a ggplot, and using geom_bar to make it a bar graph with 2 bins, one for smokers and one for non-smokers. I added colors for whether or not the person had health coverage or not. I added labels for that, changed the x label, and the title, and switched to the minimal theme. 
